Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2021-02-18 09.0_manuscript.rmd
reverted groundhog

```{r, include=FALSE, echo = FALSE}
if (!require("groundhog", quietly=TRUE)) install.packages("groundhog"); library(groundhog)
groundhog.day = "2020-04-01"
pkgs=c('knitr', 'pander', 'citr', 'broom')
suppressPackageStartupMessages(groundhog.library(pkgs, groundhog.day))
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

>>>>

```{r, include=FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
pacman::p_load(knitr, pander, citr, broom)
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```
